The Power of Unbiased Recursive Partitioning:\\ A Unifying View of CTree, MOB, and GUIDE

### 2020-01-27 pkg/partykit/inst/guideliketest/DAGStat2019/slides.Rnw
added slide for maximally selecting split variables
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/partykit@2966 255f4249-2263-4417-b1ea-8498779e27a7

Former-commit-id: 49e2087ff18d766596aa64aebdfa36202fd2b804

\documentclass[11pt,t,usepdftitle=false,aspectratio=169]{beamer}
\usetheme[license, url]{uibk}

@@

useOuterStrips(xyplot(prop_Tsplit ~ delta | variation + xi, groups = ~ test, 
                      data = subdataxi, 
                      subset = changetype == "abrupt", 
                      type = "l", lty = c(1,1,1,1),
                      lwd = 2,
                      scales=list(x=list(at=seq(1,11,2))),
                      key =  list(text = list(levels(subdataxi$test)),
                                  lines = list(lty = c(1,1,1,1), type = "l", pch = 1, cex = 0.8,
                                               col = pal[c("CTree", "MOB", "GUIDE+scores", "GUIDE")], lwd = 2)),
                      layout= c(3,2),
                      index.cond = list(c(2,3,1),c(2,1)),
                      xlab = expression(delta),
                      ylab = expression("Selection probability of"~Z[1]),
                      par.settings = par.settings),

>>>>

\documentclass[11pt,t,usepdftitle=false,aspectratio=169]{beamer}
\usetheme[url,license]{uibk}

@@

useOuterStrips(xyplot(prop_Tsplit ~ delta | variation + xi, groups = ~ test, 
                      data = subdataxi, 
                      subset = changetype == "abrupt", 
                      type = "l", lty = c(1,1,1,1),
                      lwd = 2,
                      scales=list(x=list(at=seq(1,11,2))),
                      key =  list(text = list(c(levels(subdataxi$test)," ")),
                                  lines = list(lty = c(1,1,1,1,0), type = "l", pch = 1, cex = 0.8,
                                               col = pal[c("CTree", "MOB", "GUIDE+scores", "GUIDE")], lwd = 2)),
                      layout= c(3,2),
                      index.cond = list(c(2,3,1),c(2,1)),
                      xlab = expression(delta),
                      ylab = expression("Selection probability of"~Z[1]),
                      par.settings = par.settings),

\begin{frame}%[fragile]
\frametitle{Simulation 1: Maximum vs.\ linear selection}

\begin{figure}
\setkeys{Gin}{width=0.8\linewidth}
<<scores_stump_max, fig=TRUE, echo=FALSE, height=5, width=8>>=
subdata <- subset(sim_stump, test %in% c("ctree","ctree_max","mfluc","guide_sum_12","guide_sum_1_cor"))
subdata$test <- factor(subdata$test, 
                       levels = c("ctree", "ctree_max","mfluc","guide_sum_12","guide_sum_1_cor"),
                       labels = c("CTree","CTree+max","MOB","GUIDE+scores","GUIDE"))

par.settings <- list(superpose.symbol = list(col = pal[c("CTree","CTree+max","MOB","GUIDE+scores","GUIDE")], 
                                             fill = pal[c("CTree","CTree+max","MOB","GUIDE+scores","GUIDE")]), 
                     superpose.line = list(col = pal[c("CTree","CTree+max","MOB","GUIDE+scores","GUIDE")]))

useOuterStrips(xyplot(prop_Tsplit ~ delta | variation + xi, groups = ~ test, 
                      data = subdataxi, 
                      subset = changetype == "abrupt", 
                      type = "l", lty = c(1,1,1,1,1),
                      lwd = 2,
                      scales=list(x=list(at=seq(1,11,2))),
                      key =  list(text = list(levels(subdataxi$test)),
                                  lines = list(lty = c(1,1,1,1,1), type = "l", pch = 1, cex = 0.8,
                                               col = pal[c("CTree", "CTree+max", "MOB", "GUIDE+scores", "GUIDE")], lwd = 2)),
                      layout= c(3,2),
                      index.cond = list(c(2,3,1),c(2,1)),
                      xlab = expression(delta),
                      ylab = expression("Selection probability of"~Z[1]),
                      par.settings = par.settings),
